% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
%\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadinged}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4}\\
\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Jessica Su}\\
561.543.1855\\
jtysu@stanford.edu
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
\ressubheading{Stanford University}{}{}{September 2013 - April 2018}
\begin{itemize}
\item Ph.D., Computer Science (4.0 GPA)
\item Thesis title: Recommendation Systems on Social Networks
\end{itemize}

\item \ressubheading{California Institute of Technology}{}{}{September 2007 - June 2013}
\begin{itemize}
\item B.S., Computer Science (3.8 GPA)
\end{itemize}

\end{itemize}

\resheading{Work experience (selected)}

\begin{itemize}
\item
	\ressubheading{Stanford University}{Stanford, CA}{PhD Student}{PhD Student, September 2013 - April 2018}
	\begin{itemize}
	\item Developed infrastructure to deanonymize web browsing history using publicly available Twitter data.  Successfully deanonymized 72\% of experiment participants.  You may read more about the project in The Atlantic (http://theatln.tc/2kSBZgt) and The Conversation (http://bit.ly/2DK9gVQ).
%\item  Designed an algorithm to solve the multiple-fault replacement paths problem in linear query time.
%\item Designed and implemented an algorithm to generate graphs with specific subgraph counts.
	\end{itemize}
\item
	\ressubheading{Facebook}{Seattle, WA}{Software Engineering Intern}{Software Engineering Intern, Summer 2017}
	\begin{itemize}
	\item Trained machine learning models to help Facebook understand people better, so they can show better ads.
	\end{itemize}
\item
	\ressubheading{Twitter}{San Francisco, CA}{Research Intern}{Research Intern, Summer 2015, Fall 2015, Winter 2016}
	\begin{itemize}
\item Quantified the effect of Who To Follow recommendations on the global structure of the Twitter network.  Published the results in a conference paper (``The Effect of Recommendations on Network Structure'', WWW 2016).

\item Deployed an experiment to measure the long-term effects of varying the diversity in recommendations that are shown to new users.
	\end{itemize}
%\item
%	\ressubheading{Stanford Management Science and Engineering Department}{Stanford, CA}{Research Assistant}{Research Assistant, Fall 2014 - present}
%	\begin{itemize}
%		\resitem{Developed a model to predict results of sports games from information acquired during the game. (Python, R)}
%	\end{itemize}
\item
	\ressubheading{Microsoft Research}{Mountain View, CA}{Intern}{Research Intern, Summer 2014}
	\begin{itemize}
		\resitem{Developed an algorithm to predict traits of Internet Explorer users from their browsing activity.}
	\end{itemize}
%\item
%	\ressubheading{Caltech Department of Mathematics}{Pasadena, CA}{Summer Undergraduate Research Fellow}{Summer Undergraduate Research Fellow, Summer 2011}
%	\begin{itemize}
%		\resitem{Proved that Tutte polynomials do not satisfy the Kontsevich conjecture.}
%	\end{itemize}
%\item
%	\ressubheading{FAU Department of Complex Systems and Brain Sciences}{Boca Raton, FL}%{Research Intern}{Research Intern, Winter 2010}
%	\begin{itemize}
%		\resitem{Used nonlinear differential equations to model therapist-client interactions.}
%		\resitem{Solved the equations of the model analytically.}
%	\end{itemize}

\end{itemize}

%\resheading{Projects}
%\begin{itemize}
%\item
%	\ressubheading{SKIES}{Pasadena, CA}{Intern}{Summer 2013}
%	\begin{itemize}
%		\resitem{Built image search for a collaborative education app.  (Objective-C)}
%	\end{itemize}
%
%\item
%	\ressubheading{An analysis of congressional tweets}{Pasadena, CA}{Student}{Spring 2013}
%	\begin{itemize}
%		\resitem{Scraped tweets made by congresspeople and correlated them with relevant traits of the user.  (Python, MySQL)}
%	\end{itemize}
%
%\end{itemize}

\resheading{Teaching experience}
\begin{itemize}
\item
	\ressubheading{CS 161: Design and Analysis of Algorithms}{Stanford, CA}{Instructor}{Instructor, Summer 2016}
	\begin{itemize}
	\item Taught undergraduate algorithms to a class of 111 students.  Course webpage at http://stanford.io/2xN89kO
	\item Overall quality of instruction: 4.0 out of 5.0.  (Average for previous five instructors: 3.7 out of 5.0.)
	\end{itemize}
\item
	\ressubheading{CS 161: Design and Analysis of Algorithms}{Stanford, CA}{Teaching Assistant}{Teaching Assistant (5x), Fall 2014 - Fall 2017}
\item
	\ressubheading{MS\&E 111: Introduction to Optimization}{Stanford, CA}{Teaching Assistant}{Teaching Assistant, Winter 2015}
\item
	\ressubheading{CS 224W: Social and Information Network Analysis}{Stanford, CA}{Teaching Assistant}{Teaching Assistant, Fall 2016}
\item
	\ressubheading{CS 246: Mining Massive Data Sets}{Stanford, CA}{Teaching Assistant}{Teaching Assistant, Winter 2017, Winter 2018}
\end{itemize}

\resheading{Awards}
\begin{itemize}
    \item \textbf{Outstanding TA bonus:} A \$1000 award given to the top 5\% of TAs in the department.  I won this award four quarters in a row, and was nominated for the award by three different professors (Jure Leskovec, Jeff Ullman, and Mary Wootters).
	\item \textbf{Stanford School of Engineering Fellowship} (2013, one year of funding)
%	\item Top 500 Putnam (2008)
	\item \textbf{Lingle Scholarship} (2007, awarded to top two freshmen in incoming class)
	\item \textbf{Axline Scholarship} (2007, full ride merit scholarship)
\end{itemize}

\resheading{Publications}
\begin{itemize}
\item \textbf{Su J}, Shukla A, Goel S, and Narayanan A.  De-anonymizing Web Browsing Data with Social Networks.  WWW 2017.
  \item \textbf{Su J}, Sharma A, and Goel S.  The Effect of Recommendations on Network Structure.  WWW 2016.
	\item Marcolli M and \textbf{Su J} (2013) Arithmetic of Potts Model Hypersurfaces.  International Journal of Geometric Methods in Modern Physics 10-4.  arXiv:1112.5667 [math-ph].
	\item Liebovitch L, Peluso P, Norman M, \textbf{Su J}, Gottman J (2011) Mathematical model of the dynamics of psychotherapy.  Cognitive Neurodynamics 1-11.
	\item Peluso P, Liebovitch L, Gottman J, \textbf{Su J} (2011) A mathematical model of psychotherapy: an investigation using dynamic non-linear equations to model the therapeutic relationship.  Psychotherapy Research.
	\item Ward C, \textbf{Su J}, Huang Y, Lloyd A, Gould F, Hay B (2011) Medea selfish genetic elements as tools for altering traits of wild populations: a theoretical analysis.  Evolution 65:1149-1162.
	\item Hay B, Chen CH, Ward CM, Huang H, \textbf{Su JT}, Guo M (2010) Engineering the genomes of wild insect populations: Challenges, and opportunities provided by synthetic Medea selfish genetic elements.  Journal of Insect Physiology 56(10):1402-1413.
	\item Chen CH, Huang H, Ward CM, \textbf{Su JT}, Schaeffer LV, Guo M, Hay BA (2007) A synthetic maternal-effect selfish genetic element drives population replacement in Drosophila. Science 316:597-600.
%	\item Norman M, Liebovitch L, Peluso P, \textbf{Su J}, Gottman J.  Mathematical Model of the Dynamics of Psychotherapy.  International Conference on Complex Systems, June 2011, Cambridge MA.
%	\item Liebovitch L, Peluso P, \textbf{Su J}, Gottman J. 2010. Mathematical Model of Psychotherapy - A New Approach to Understanding the Therapeutic Relationship. Association for Psychological Science, May 29, 2010, Boston MA.
\end{itemize}

\resheading{Other activities}
\begin{itemize}
\item Reviewer, WWW 2018, Poster Track
\item Reviewer, WWW 2017, Poster Track
\end{itemize}

\end{document}
